---
title: "new R assignment"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Q1 - Introduction 
You own a supermarket mall and through membership cards , you have some basic data about your customers like Customer ID, age, gender, annual income and spending score.
Spending Score is something you assign to the customer based on your defined parameters like customer behavior and purchasing data.
You own the mall and want to understand the customers like who can be easily converge [Target Customers] so that the sense can be given to marketing team and plan the strategy accordingly.

```{r cars, echo=TRUE}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=TRUE}


```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=TRUE}
plot(pressure)
```

## Q2 
str(Mall)

## Q3 
names(Mall)

## Q4
head(Mall, n=15)

##Q5
sum_of_square <- function(x,y) {x^2 + y^2}

sum_of_square(3,4)

## convert columns from chr to num before applying function
 Mall$V1 <- as.numeric(Mall$V1)

## Check if first column was converted correctly
str(Mall$V1)
## covert other columns to num

Mall$V4 <- as.numeric(Mall$V3)
Mall$V5 <- as.numeric(Mall$V5)


## Check if second column was converted correctly
str(Mall$V3)

## Q6
as.data.frame(Mall %>% select(1:3))

# Q7

# Q8
Mall %>% drop_na()

# Q9
Mall %>% distinct()

##Q10
Mall %>% arrange(desc(V4))

Mall %>% arrange(desc(V3))

#Q11
names(Mall)[names(Mall) == "V3"] <- "age" 
names(Mall)[names(Mall) == "V4"] <- "income" 
head(Mall, n=15)

#Q12
## Convert chr to num
Mall$age <- as.numeric(Mall$age)
Mall$income <- as.numeric(Mall$income)
str(Mall$income)
## add new column
Mall %>% mutate(Newcol = income/age)

#Q13
set.seed(5) 
TrainingSet <- sort(sample.int(100, 50))
TrainingSet

#Q14
Mall %>% group_by(V2) %>% summarise(mean(income))

#Q15
#change the value of the first row in colum'age' to 0 because it is showing up as na
Mall$age[0]
head(Mall, n=3)

Mall$age[1] =0
# check to see that value is changed
Mall$age[1]
Mall$age[2]
# perform mean operation
mean(Mall$age)

#Q16
ggplot(Mall, aes(Mall$V5, y=Mall$income)) +
  geom_point(size=2, shape=23)
  
# Q17
ggplot(data=Mall, aes(x=Mall$V2, y=Mall$age)) +
  geom_bar(stat="identity")

# Q18
fit <- lm(Mall$age ~ Mall$V5)
fit


